Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-06-01 paper_aimsa/results.tex
finally

how well it worked, plots, ...

>>>>

RL_POWER Gaits
The results for the gaits evolved by RL_POWER are shown
in Figure 8 and Table 2. A total of 900 evaluations were performed for HyperNEAT (300 in each of three runs). Overall the RL_POWER gaits were the faster and more stable by far, beating the HyperNEAT when comparing either average or best gaits

(pic)RL_POWER AND HyperNEAT performance chart

or best gaits. We believe that this is because RL_POWER uses evolvable splines to represent gaits As explained earlier,  
The single best gait found during this study had a speed of
XXXX body lengths/minute, XX%
better than the best HyperNEAT gait. Figure 9 shows a typical RL_POWER gait that had high fitness. The pattern of motion is less complex and more regular than the HyperNEAT, in that patterns of multiple motors are coordinated.
A corresponding observation of this property is that the noisiness of RL_POWER is significantly lower than that of HyperNEAT. One reason of this is that the when Expectation Maximization methodology is used, explorations happened in the vicinity space of the highest ranked patterns. Even some individual HyperNEAT gaits turned out very effective, the average noisiness of HyperNEAT is very large. For example, as found in [xx], the mean of HyperNEAT generation-champion’s performance was XX body lengths/minute (+-XX SD), but it had a max of 38 and a min of 3. RL_POWER, on the other hand,  proved to be stable and much less noisy throughout the entire experiment. The maximum SD over all three runs is +- XX SD. This may also be due to a much larger space of possibilities of HyperNEAT than the more heuristically guided reinforcement learning.

[pic][speed chart of two algos]
